Object naming is context dependent - A case study on testing linguistic hypotheses on real-world image corpora

### 2018-07-12 papers/SiVL2018/resources.tex
modifies Table w/ ILVSRC/WordNet cmp

\begin{table}[t]
	\begin{tabular}{lrrrr}
		\hline
			 			& \refcoco & \refcocop & \flickr & \vgenome \\
		\hline \hline
		total \#synsets	&	2580\\
		- match			&	112 \\
		- hyponyms		&	36 \\
		- hypernyms 	&	204 \\
		\hline
		%- not found		&	74 \\	
		%\hline
		\# 
				& \multicolumn{3}{c}{No. object names $obj$ for which $*(\text{synset}(obj), \text{ILSVRC})$:} \\
				& (obj)
				& in
				& hypernym
				& hyponym\\
		\hline \hline
		 	& 2580 & 112 & 204 & 36\\
		 	& 15 & 30 & 1 \cs{??}\\
		 	& \\
		\vgenome 	& \\
		\hline
	\end{tabular}
	\caption{Coverage of the object names in the datasets by WordNet and by the $1,000$~synsets of the ILSVRC image classification challenge. \#synsets(obj): number of object names for which synsets could be retrieved from WordNet;   \label{tab:coverage_ilsvrc}}
\end{table}

>>>>

\begin{table}[t]
	\begin{center}
	\begin{tabular}{l|r|rrr}
		\hline
				& \#synset($obj$) 
				& \multicolumn{3}{c}{\#$obj$ for which $*(\text{synset}(obj), \text{ILSVRC})$} \\
				&
				& in
				& hypernym
				& hyponym\\
		\hline \hline
		 \refcoco  (REs)		& 2,580 & 112 	& 204 	& 36\\
		 \refcoco (categories)	& 78	& 15 	& 30 	& 1 (?) \\
		\vgenome 	& \\
		\flickr					& 6,139 & 238	& 338	& 95\\
		\hline
	\end{tabular}
	\caption{Coverage of the unique object names (obtained from the categories or  from the REs) in the datasets by WordNet (first column) and by the $1,000$~synsets of the ILSVRC image classification challenge (columns~2--4).  \#synsets($obj$): no. names for which synsets could be retrieved from WordNet;   \label{tab:coverage_ilsvrc}}
	\end{center}
\end{table}
